Consensus Problems in Networks of Agents\\ with Switching Topology and Time-Delays

### 2020-10-30 Paper.tex
Fixed errors

假设图的每一个节点都是一个具有动态性能的动态智能体
\begin{equation}
    \dot{x}_i = f(x_i, u_i), i\in \mathcal{I}
    \tag{2}
    \label{2}
\end{equation}
{\color[gray]{0.5}
\noindent A dynamic graph (or dynamic network) is deﬁned as a 4-tuple $G_{x(t)} = (\mathcal{V},\mathcal{E},\mathcal{A},x(t))$ together with dynamics $\dot{x}=F(x,u)$ where $x$ denotes the state of the dynamic graph and {\color{green}$F(x,u)$ is the column-wise concatenation of the elements $F_i(x,u)=f(x_i,u_i)$}.
}

@@

定义$\chi: \mathbb{R}^n \rightarrow \mathbb{R}$是一个包含$n$个变量$x_1,\dots,x_n$的函数。
在一个动态图中的$\chi$-一致性问题，是通过利用输入$u_i$以一种分布式的方式来计算$\chi(x(0))$，其中输入$u_i$仅依赖于节点$i$的和它的邻居的值。
我们定义一个协议
\begin{equation}
    u_i = k_i(x_{j_1},\dots,x_{j_{m_i}})
    \tag{3}
    \label{3}
\end{equation}
{\color[gray]{0.5}
\noindent with $j_1,\dots,j_{m_i}\in \{i\} \cup N_i$ and $m_i\leq n$ asymptotically solves the $\chi$ -consensus problem if and only if there exists an asymptotically stable equilibrium $x^*$ of $\dot{x}=F(x,k(x))$ such that $x^*=\chi(x(0))$ for all $i\in \mathcal{I}$. 
We are interested in solving the $\chi$ -consensus problem in a distributed fashion in which {\color{green}no node is connected to all other nodes (i.e. $m_i < n$ for all $i$)}.
}

@@

\noindent 这一部分，我们介绍了三种一致性协议，分别用来解决连续时间（continuous-time，CT）动态积分器智能体
\begin{equation}
    \dot{x}_i(t) = u_i(t)
    \tag{4}
    \label{4}
\end{equation}
% \begin{equation}
%     \text{\color{userColor}位置状态的一阶导数 = 输入}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent or agents with discrete-time (DT) model
}

\noindent 和离散时间（discrete-time，DT）动态智能体模型的网络一致性问题，
\begin{equation}
    x_i(k+1) = x_i(k)+\epsilon u_i(k)
    \tag{5}
    \label{5}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{ 下一时刻的状态 = 此刻的状态 + }\epsilon \text{ * 此时的输入}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent and step-size $\epsilon>0$. 
In this paper, we consider three scenarios:
}

@@

i）固定或切换拓扑的零通信时滞：我们使用下边的线性一致性协议：
\begin{equation}
    u_i = \sum_{j\in N_i}a_{ij}(x_j-x_i)
    \tag{A1}
    \label{A1}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{控制输入 = 对所有的\ 节点j和i的位置差值 * 两节点的权重\ 求和，其中j是所有i的邻居节点}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent where the set of neighbors $N_i=N_i(G)$ of node $i$ is variable in networks with switching topology.
}

@@

ii）固定拓扑$G=(\mathcal{V}, \mathcal{E}, \mathcal{A})$和对应于边$ij\in \mathcal{E}$的通信时滞$\tau_{ij}>0$：我们使用下边的线性时滞一致性协议：
\begin{equation}
    u_i(t) = \sum_{j\in N_i}a_{ij}[x_j(t-\tau_{ij})-x_i(t-\tau_{ij})]
    \tag{A2}
    \label{A2}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{控制输入 = 对所有的\ 节点j和i的位置差值（减去时滞） * 两节点的权重\ 求和，其中j是所有i的邻居节点}
%     \notag
% \end{equation}

@@

所给的协议（A1），连续时间网络的智能体状态会随着下面的线性系统进行变化
\begin{equation}
    \dot{x}(t) = -Lx(t) 
    \tag{6}
    \label{6}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{位置状态的一阶导数 = 拉普拉斯矩阵 * 位置状态值}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent where L is called the graph Laplacian induced by the information ﬂow G and is deﬁned by
}

\noindent 这里，$L$是信息流网络$G$的图拉普拉斯矩阵，并且定义如下
\begin{equation}
l_{ij} = \left\{
    \begin{array}{ll}
        \sum_{k=1,k\ne i}^n a_{ik}, & j=i\\
        -a_{ij}, & j\ne i
    \end{array}\right.
    \tag{7}
    \label{7}
\end{equation}
{\color[gray]{0.5}
\noindent The properties of graph Laplacian is one of the main areas of research in algebraic graph theory and is discussed in Section 4.
}

@@

在一个切换拓扑（switching topology）网络中，协议(\ref{A1})的收敛性分析等价于混合系统（hybrid system）的稳定性分析
\begin{equation}
    \dot{x}(t) = -L_kx(t),\ k=s(t) 
    \tag{8}
    \label{8}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{位置状态的一阶导数 = 拉普拉斯矩阵（关于切换信号变换） * 位置状态值}
%     \notag
% \end{equation}
{\color[gray]{0.5}
\noindent where $L_k = \mathcal{L}(G_k)$ is the Laplacian of $G_k$, $s(t)$ : $\mathbb{R}\rightarrow \mathcal{I} \subset \mathbb{Z}$ is a switching signal, and {\color{green}$\Gamma\ni G_k$ is a ﬁnite collection of digraphs (of order $n$) with the index set $\mathcal{I}_\Gamma$}. 
Later, we will see that $\Gamma$ is a relatively large set for $n\gg 1$. 
The task of stability analysis for the hybrid system in (8) is rather challenging partly because, in general, the product of two Laplacian matrices do not commute.
}

@@

对于离散时间的智能体模型，应用协议(\ref{A1})给出了如下的动态离散网络
\begin{equation}
    x(k+1) = P_\epsilon x(k)
    \tag{9}
    \label{9}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{ 下一时刻的状态 = 非负随机矩阵 * 此刻的状态}
%     \notag
% \end{equation}

@@

\noindent 其中
\begin{equation}
    P_\epsilon = I - \epsilon L
    \tag{10}
    \label{10}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{ 非负随机矩阵 = 单位矩阵 - }\epsilon \text{ * 拉普拉斯矩阵}
%     \notag
% \end{equation}
\noindent Let $d_{max} = \max_il_{ii}$, then for $\epsilon\in (0,1/d_{max})$, $P_\epsilon$ is a nonnegative and stochastic matrix that we call Perron matrix, i.e. $P_\epsilon$ in element-wise nonnegative and all of its row sums are 1.

@@

\begin{equation}
    L = \mathcal{L}(G) = \Delta-\mathcal{A}
    \tag{12}
    \label{12}
\end{equation}
% \begin{equation}
%     \color{userColor}\text{这和之前参考的文献中的关于拉氏矩阵定义的阐述一致} L = D - A
%     \notag
% \end{equation}

@@

{\color[gray]{0.5}
\noindent \textbf{Theorem} 2. (spectral localization) Let $G=(\mathcal{V},\mathcal{E},\mathcal{A})$ be a digraph with the Laplacian $L$. 
Denote the maximum node out-degree of $G$ by $d_{max}(G) = \max_i \deg_{out}(v_i)$. 
Then, all the eigenvalues of $L=\mathcal{L}(G)$ are located in the following disk
}

\noindent \textbf{Theorem} 2. (spectral localization) 定义$G=(\mathcal{V},\mathcal{E},\mathcal{A})$是关于拉普拉斯矩阵$L$的加权有向图。
记图$G$的节点的最大化出度为$d_{max}(G) = \max_i \deg_{out}(v_i)$。
那么，所有的$L=\mathcal{L}(G)$的特征值都位于下面的圆盘中

@@

\noindent \textbf{Proof.} 基于圆盘定理，所有$L=[l_{ij}]$的特征值都位于下面的$n$个圆盘的并集中
\begin{equation}
    D_i = \{ z\in \mathbb{C}: |z-l_{ii}| \le \sum_{j\in \mathcal{I},j\ne i}|l_{ij}| \}
    \tag{16}
    \label{16}
\end{equation}

{\color[gray]{0.5}
But l ii = ∆ ii and
}

@@

对于图$G=(\mathcal{V}, \mathcal{E})$，$\sum_{i=1}^{3}u_i = x_3 - x_1$。
因此，如果节点1和3不一致，那么属性$\sum_{i=1}^{3}u_i = 0$不是对于所有的$x$都成立。
另一方面，读者可以在本例中来验证这一点

@@

在提出我们第一次的主要结果之前，我们需要提出一个指数矩阵如$e^{(-Lt)}$形式的极限理论。
这是因为系统(\ref{6})的解决办法是通过以下公式给出

>>>>

假设图的每一个节点都是一个具有动态性能的动态智能体

\begin{equation}
    \dot{x}_i = f(x_i, u_i), i\in \mathcal{I}
    \tag{2}
    \label{2}
\end{equation}

{\color[gray]{0.5}
\noindent A dynamic graph (or dynamic network) is deﬁned as a 4-tuple $G_{x(t)} = (\mathcal{V},\mathcal{E},\mathcal{A},x(t))$ together with dynamics $\dot{x}=F(x,u)$ where $x$ denotes the state of the dynamic graph and {\color{green}$F(x,u)$ is the column-wise concatenation of the elements $F_i(x,u)=f(x_i,u_i)$}.
}

@@

定义$\chi: \mathbb{R}^n \rightarrow \mathbb{R}$是一个包含$n$个变量$x_1,\dots,x_n$的函数。
在一个动态图中的$\chi$-一致性问题，是通过利用输入$u_i$以一种分布式的方式来计算$\chi(x(0))$，其中输入$u_i$仅依赖于节点$i$的和它的邻居的值。
我们定义一个协议

\begin{equation}
    u_i = k_i(x_{j_1},\dots,x_{j_{m_i}})
    \tag{3}
    \label{3}
\end{equation}

{\color[gray]{0.5}
\noindent with $j_1,\dots,j_{m_i}\in \{i\} \cup N_i$ and $m_i\leq n$ asymptotically solves the $\chi$ -consensus problem if and only if there exists an asymptotically stable equilibrium $x^*$ of $\dot{x}=F(x,k(x))$ such that $x^*=\chi(x(0))$ for all $i\in \mathcal{I}$. 
We are interested in solving the $\chi$ -consensus problem in a distributed fashion in which {\color{green}no node is connected to all other nodes (i.e. $m_i < n$ for all $i$)}.
}

@@

\noindent 这一部分，我们介绍了三种一致性协议，分别用来解决连续时间（continuous-time，CT）动态积分器智能体

\begin{equation}
    \dot{x}_i(t) = u_i(t)
    \tag{4}
    \label{4}
\end{equation}

% \begin{equation}
%     \text{\color{userColor}位置状态的一阶导数 = 输入}
%     \notag
% \end{equation}

{\color[gray]{0.5}
\noindent or agents with discrete-time (DT) model
}

\noindent 和离散时间（discrete-time，DT）动态智能体模型的网络一致性问题，

\begin{equation}
    x_i(k+1) = x_i(k)+\epsilon u_i(k)
    \tag{5}
    \label{5}
\end{equation}

% \begin{equation}
%     \color{userColor}\text{ 下一时刻的状态 = 此刻的状态 + }\epsilon \text{ * 此时的输入}
%     \notag
% \end{equation}

{\color[gray]{0.5}
\noindent and step-size $\epsilon>0$. 
In this paper, we consider three scenarios:
}

@@

i）固定或切换拓扑的零通信时滞：我们使用下边的线性一致性协议：

\begin{equation}
    u_i = \sum_{j\in N_i}a_{ij}(x_j-x_i)
    \tag{A1}
    \label{A1}
\end{equation}

% \begin{equation}
%     \color{userColor}\text{控制输入 = 对所有的\ 节点j和i的位置差值 * 两节点的权重\ 求和，其中j是所有i的邻居节点}
%     \notag
% \end{equation}

{\color[gray]{0.5}
\noindent where the set of neighbors $N_i=N_i(G)$ of node $i$ is variable in networks with switching topology.
}

@@

ii）固定拓扑$G=(\mathcal{V}, \mathcal{E}, \mathcal{A})$和对应于边$ij\in \mathcal{E}$的通信时滞$\tau_{ij}>0$：我们使用下边的线性时滞一致性协议：

\begin{equation}
    u_i(t) = \sum_{j\in N_i}a_{ij}[x_j(t-\tau_{ij})-x_i(t-\tau_{ij})]
    \tag{A2}
    \label{A2}
\end{equation}

% \begin{equation}
%     \color{userColor}\text{控制输入 = 对所有的\ 节点j和i的位置差值（减去时滞） * 两节点的权重\ 求和，其中j是所有i的邻居节点}
%     \notag
% \end{equation}

@@

所给的协议（A1），连续时间网络的智能体状态会随着下面的线性系统进行变化

\begin{equation}
    \dot{x}(t) = -Lx(t) 
    \tag{6}
    \label{6}
\end{equation}

% \begin{equation}
%     \color{userColor}\text{位置状态的一阶导数 = 拉普拉斯矩阵 * 位置状态值}
%     \notag
% \end{equation}

{\color[gray]{0.5}
\noindent where L is called the graph Laplacian induced by the information ﬂow G and is deﬁned by
}

\noindent 这里，$L$是信息流网络$G$的图拉普拉斯矩阵，并且定义如下

\begin{equation}
l_{ij} = \left\{
    \begin{array}{ll}
        \sum_{k=1,k\ne i}^n a_{ik}, & j=i\\
        -a_{ij}, & j\ne i
    \end{array}\right.
    \tag{7}
    \label{7}
\end{equation}

{\color[gray]{0.5}
\noindent The properties of graph Laplacian is one of the main areas of research in algebraic graph theory and is discussed in Section 4.
}

@@

在一个切换拓扑（switching topology）网络中，协议(\ref{A1})的收敛性分析等价于混合系统（hybrid system）的稳定性分析

\begin{equation}
    \dot{x}(t) = -L_kx(t),\ k=s(t) 
    \tag{8}
    \label{8}
\end{equation}

% \begin{equation}
%     \color{userColor}\text{位置状态的一阶导数 = 拉普拉斯矩阵（关于切换信号变换） * 位置状态值}
%     \notag
% \end{equation}

{\color[gray]{0.5}
\noindent where $L_k = \mathcal{L}(G_k)$ is the Laplacian of $G_k$, $s(t)$ : $\mathbb{R}\rightarrow \mathcal{I} \subset \mathbb{Z}$ is a switching signal, and {\color{green}$\Gamma\ni G_k$ is a ﬁnite collection of digraphs (of order $n$) with the index set $\mathcal{I}_\Gamma$}. 
Later, we will see that $\Gamma$ is a relatively large set for $n\gg 1$. 
The task of stability analysis for the hybrid system in (8) is rather challenging partly because, in general, the product of two Laplacian matrices do not commute.
}

@@

对于离散时间的智能体模型，应用协议(\ref{A1})给出了如下的动态离散网络

\begin{equation}
    x(k+1) = P_\epsilon x(k)
    \tag{9}
    \label{9}
\end{equation}

% \begin{equation}
%     \color{userColor}\text{ 下一时刻的状态 = 非负随机矩阵 * 此刻的状态}
%     \notag
% \end{equation}

@@

\noindent 其中

\begin{equation}
    P_\epsilon = I - \epsilon L
    \tag{10}
    \label{10}
\end{equation}

% \begin{equation}
%     \color{userColor}\text{ 非负随机矩阵 = 单位矩阵 - }\epsilon \text{ * 拉普拉斯矩阵}
%     \notag
% \end{equation}

\noindent Let $d_{max} = \max_il_{ii}$, then for $\epsilon\in (0,1/d_{max})$, $P_\epsilon$ is a nonnegative and stochastic matrix that we call Perron matrix, i.e. $P_\epsilon$ in element-wise nonnegative and all of its row sums are 1.

@@

\begin{equation}
    L = \mathcal{L}(G) = \Delta-\mathcal{A}
    \tag{12}
    \label{12}
\end{equation}

% \begin{equation}
%     \color{userColor}\text{这和之前参考的文献中的关于拉氏矩阵定义的阐述一致} L = D - A
%     \notag
% \end{equation}

@@

{\color[gray]{0.5}
\noindent \textbf{Theorem 2.} (spectral localization) Let $G=(\mathcal{V},\mathcal{E},\mathcal{A})$ be a digraph with the Laplacian $L$. 
Denote the maximum node out-degree of $G$ by $d_{max}(G) = \max_i \deg_{out}(v_i)$. 
Then, all the eigenvalues of $L=\mathcal{L}(G)$ are located in the following disk
}

\noindent \textbf{Theorem 2.} (spectral localization) 定义$G=(\mathcal{V},\mathcal{E},\mathcal{A})$是关于拉普拉斯矩阵$L$的加权有向图。
记图$G$的节点的最大化出度为$d_{max}(G) = \max_i \deg_{out}(v_i)$。
那么，所有的$L=\mathcal{L}(G)$的特征值都位于下面的圆盘中

@@

\noindent \textbf{Proof.} 基于圆盘定理，所有$L=[l_{ij}]$的特征值都位于下面的$n$个圆盘的并集中

\begin{equation}
    D_i = \{ z\in \mathbb{C}: |z-l_{ii}| \le \sum_{j\in \mathcal{I},j\ne i}|l_{ij}| \}
    \tag{16}
    \label{16}
\end{equation}

{\color[gray]{0.5}
But $l_{ii} = \Delta_{ii}$ and
}

@@

对于图$G=(\mathcal{V}, \mathcal{E})$，$\sum_{i=1}^{3}u_i = x_3 - x_1$。
因此，如果节点1和3状态不相等，那么$\sum_{i=1}^{3}u_i = 0$不是对于所有的$x$都成立。
另一方面，读者可以在本例中来验证这一点

@@

在提出我们第一次的主要结果之前，我们需要提出一个指数矩阵如$e^{(-Lt)}$形式的极限理论。
这是因为公式(\ref{6})的解决办法是通过以下公式给出
